% Please keep it to 80 columns, no tabs, no trailing whitespace
% and no Windows line endings (\r\n)

\documentclass[10pt,oneside,landscape,notitlepage]{report}
\usepackage[a3paper]{geometry}
\usepackage{tabularx}
\usepackage[cm]{fullpage}
\usepackage{color}

\begin{document}
\color{white}
\pagecolor{black}
\clearpage
\thispagestyle{empty}
 \begin{tabularx}{\textwidth}{| L | X | L | L | X | X |}
   \hline

   Name & Description & Language & License & Links & Comments \\
   \hline
   Yi & Text editor written in and using Haskell for configuration & Haskell &
   GPL & https://github.com/yi-editor/yi & Not usable day-to-day but has a lot
   of potential. Configs available for vim and emacs users. \\
   \hline
   Clementine & Cross-platform (Linux, OSX, Windows) music player picking up
   where Amarok 1.4 left. All code was rewritten. Uses gstreamer as a backend. &
   C++ & GPLv3 & http://code.google.com/p/clementine-player/issues/list & There
   are many issues open and quite a few of them are fairly easy to fix. Attach
   patches on relevant issues. Uses Qt4 for front-end. Ask in DPTs for help on
   picking issues.\\
   \hline
   Haddock & Haskell's documentation engine & Haskell & BSD3 &
   http://trac.haskell.org/haddock/report/1 & Many issues, mostly involving
   output formats. Hoogle back-end quite broken, \LaTeX back-end needs tests and
   probably also severely broken by now. Ask in the DPTs for help. A bit hard to
   get your code upstream due to tight binding with GHC. Needs GHC HEAD to hack
   on. \\
   \hline
   GHC & Haskell compiler & Haskell & GHC License &
   https://ghc.haskell.org/trac/ghc/ \newline
   https://ghc.haskell.org/trac/ghc/wiki/WorkingConventions \newline
   http://www.haskell.org/ghc/license \newline
   https://ghc.haskell.org/trac/ghc/wiki/Newcomers &
   Don't be intimidated by the fact that it's a compiler. Haskell programs are
   very self contained and it's quite easy to get started on something. Somewhat
   tiresome to work with due to large tree and long validation process. Look for
   getting started guides on the GHC wiki. Subscribe to GHC mailing lists. \\
   \hline
   Yon-chan & emacs 4chan browser & Emacs Lisp & GPLv3 &
   https://github.com/davexunit/yon-chan & Very incomplete but would be very
   useful for those of us who don't like leaving emacs. There should be few
   commits going its way Soon\texttrademark. Ask in DPTs for help. \\
   \hline
   mentor & emacs interface to rtorrent & Emacs Lisp & GPLv3 &
   https://github.com/skangas/mentor & Performance is absolute ass for many
   torrents, locks up your whole emacs while fetching data. No local socket
   support. \\
   \hline
   screenFetch & System information tool & Bash & GPLv3 &
   https://github.com/KittyKatt/screenFetch & It's 3000 lines of Bash, shouldn't
   really need a comment. In dire need of some test environment. Check the
   issues. It's in Bash because close to every GNU/Linux machine will
   have it installed. \\
   \hline
   guile-2d & 2D game library & Guile & LGPLv3 &
   https://github.com/davexunit/guile-2d & Check TODO.org \\
   \hline
   hspec & Testing framework for Haskell, bit like RSpec for Ruby. & Haskell &
   MIT & https://github.com/hspec/hspec/issues & Issue #103 would be nice.
   Discuss with maintainer beforehand, he's a cool guy. \\
   \hline
   xmobar & Status bar & Haskell & BSD3 &
   http://code.google.com/p/xmobar/issues/list & Sign up to mailing list. Could
   always use more plugins. Source is hosted on GitHub where you can also find
   more issues. \\
   \hline
   xmonad & Tiling WM & Haskell & BSD3 &
   http://code.google.com/p/xmonad/issues/list & Also check out xmonad-contrib
   \\
   \hline
   Hackage 2 & Haskell package repository & Haskell & BSD3 &
   https://github.com/haskell/hackage-server/issues & Recently deployed.
   Maintainers always look for some hands to write some code. Check out \#hackage
   on Freenode. \\
   \hline
   Cabal & Haskell package installer & Haskell & BSD3 &
   https://github.com/haskell/cabal & Issues range from summer projects to a day
   of hacking. \\
   \hline
   ghc-android & Build scripts for compiling Haskell to Android & Haskell
   patches and C & Same as GHC & https://github.com/neurocyte/ghc-android &
   No one wants to write Java. \\
   \hline
   gemrb & Implementation of the Infinity Engine & C++ engine, Python scripting
   & GPLv2 & https://github.com/gemrb/gemrb & An old but still active project.
   Infinity Engine    is what Icewind Dale, Baldur's Gate and other such games
   use. Guides to hacking in the repo. \\
   \hline
   attoparsec & Haskell library for parsing & Haskell & BSD3 &
   https://github.com/bos/attoparsec/issues?state=open & Like Parsec but
   sacrificing nice errors and some combinators for speed. Should be fairly easy
   fixes for the most part. \\
   \hline
   mplayer-mode & emacs mode for mplayer control & Emacs Lisp & GPLv3 &
   https://github.com/markhepburn/mplayer-mode & No open issues but is rather
   featureless. Needs testing for compatibility with mplayer2 and emacs24. More
   functions and customisable settings would be nice. \\
   \hline
   magit & emacs mode for git interaction & Emacs Lisp & GPLv3 &
   https://github.com/magit/magit & If you're an emacs user and don't know what
   magit is then I feel sorry for you. Mostly minor fixes and feature requests.
   \\
   \hline
   colobot & FOSS version of an old educational game using C++-like language to
   control robots & C++ & GPLv3 & https://github.com/colobot/colobot & Last time
   I checked, it ran worse on my Core 2 Duo 1.8GHz than the original version on
   my Pentium 233MHz. Check the open issues. \\
   \hline
   distributed-haskell & Cloud Haskell & Haskell & BSD3 &
   https://github.com/haskell-distributed/distributed-process \newline
   https://cloud-haskell.atlassian.net/secure/Dashboard.jspa &
   Project split into multiple repositories, check the GitHub user \\
   \hline
   magit-gh-pulls & Extends magit to deal with GitHub pull requests & Emacs Lisp
   & GPLv3(?) & https://github.com/sigma/magit-gh-pulls & Last time I checked it
   was completely broken. Needs fixing. \\
   \hline
   yukari & Haskell library + executable for AnimeBytes automation & Haskell &
   GPLv3 & https://github.com/Fuuzetsu/yukari & Still working on it, could use
   some hands to help me though. Pretty horrible still. \\
   \hline
   torrentinfo & torrent file reading & Python & GPLv2 &
   https://github.com/Fuuzetsu/torrentinfo & At this point just needs adding
   features. Check open issues. Make sure to update docs and tests if hacking on
   it. \\
   \hline





 \end{tabularx}
\end{document}
